Plots and tables summarizing results of Poisson simulations

### 2020-06-26 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

This plot shows the function used to simulate the "Spikes" data sets
at the $(1/100, 3)$ intensity range, along with an example data set
(black circles), and example fitted curves produced by the SMASH and
Haar-Fisz methods:

@@

This is the function used to simulate the "Angles" data sets at
different ranges of intensities:

```{r plot-angles-function, fig.height=2.5, fig.width=8}
mu.ang <- 0.01 + angles.f(t)
x <- rpois(n,mu.ang)
p2 <- create.signal.plot(t,x,mu.ang)
print(p2)
```

@@

This is the function used to simulate the "Heavisine" data sets at
different ranges of intensities:

```{r plot-heavisine-function, fig.height=2.5, fig.width=8}
mu.hs <- 0.01 + heavi.f(t)
x <- rpois(n,mu.hs)
p3 <- create.signal.plot(t,x,mu.hs)
print(p3)
```

@@

This is the function used to simulate the "Bursts" data sets at
different ranges of intensities:

```{r plot-bursts-function, fig.height=2.5, fig.width=8}
mu.bur <- 0.01 + bursts.f(t)
x <- rpois(n,mu.bur)
p4 <- create.signal.plot(t,x,mu.bur)
print(p4)
```

@@

This is the function used to simulate the "Clipped Blocks" data sets at
different ranges of intensities:

```{r plot-cb-function, fig.height=2.5, fig.width=8}
mu.cb <- 0.01 + cblocks.f(t)
x <- rpois(n,mu.cb)
p5 <- create.signal.plot(t,x,mu.cb)
print(p5)
```

@@

This is the function used to simulate the "Bumps" data sets at
different ranges of intensities:

```{r plot-bumps-function, fig.height=2.5, fig.width=8}
mu.b <- 0.01 + bumps.f(t)
x <- rpois(n,mu.b)
p6 <- create.signal.plot(t,x,mu.b)
print(p6)
```

>>>>

This plot shows the function used to simulate the "Spikes" data sets
at the $(1/100, 3)$ intensity range. We also show an example data set
simulated from the Spikes intensity function (black circles), and the
fitted curves obtained by applying SMASH (orange) and the Haar-Fisz
method (light blue) to these data:

@@

This is the function used to simulate the "Angles" data sets at
different ranges of intensities. We also show an example data set
simulated from the Angles intensity function (black circles), and the
fitted curves obtained by applying SMASH (orange) and the Haar-Fisz
method (light blue) to these data:

```{r plot-angles-function, fig.height=2.5, fig.width=8}
mu.ang    <- 0.01 + angles.f(t)
x         <- rpois(n,mu.ang)
out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
out.smash <- smash.poiss(x,post.var = TRUE)
p2 <- create.signal.plot(t,x,mu.ang) +
  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
print(p2)
```

@@

This is the function used to simulate the "Heavisine" data sets at
different ranges of intensities. We also show an example data set
simulated from the Heavisine intensity function (black circles), and
the fitted curves obtained by applying SMASH (orange) and the
Haar-Fisz method (light blue) to these data:

```{r plot-heavisine-function, fig.height=2.5, fig.width=8}
mu.hs     <- 0.01 + heavi.f(t)
x         <- rpois(n,mu.hs)
out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
out.smash <- smash.poiss(x,post.var = TRUE)
p3 <- create.signal.plot(t,x,mu.hs) +
  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
print(p3)
```

@@

This is the function used to simulate the "Bursts" data sets at
different ranges of intensities. We also show an example data set
simulated from the Bursts intensity function (black circles), and the
fitted curves obtained by applying SMASH (orange) and the Haar-Fisz
method (light blue) to these data:

```{r plot-bursts-function, fig.height=2.5, fig.width=8}
mu.bur    <- 0.01 + bursts.f(t)
x         <- rpois(n,mu.bur)
out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
out.smash <- smash.poiss(x,post.var = TRUE)
p4 <- create.signal.plot(t,x,mu.bur) +
  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
print(p4)
```

@@

This is the function used to simulate the "Clipped Blocks" data sets
at different ranges of intensities. We also show an example data set
simulated from the Clipped Blocks intensity function (black circles),
and the fitted curves obtained by applying SMASH (orange) and the
Haar-Fisz method (light blue) to these data:

```{r plot-cb-function, fig.height=2.5, fig.width=8}
mu.cb     <- 0.01 + cblocks.f(t)
x         <- rpois(n,mu.cb)
out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
out.smash <- smash.poiss(x,post.var = TRUE)
p5 <- create.signal.plot(t,x,mu.cb) +
  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
print(p5)
```

@@

This is the function used to simulate the "Bumps" data sets at
different ranges of intensities. We also show an example data set
simulated from the Bumps intensity function (black circles), and the
fitted curves obtained by applying SMASH (orange) and the Haar-Fisz
method (light blue) to these data:

```{r plot-bumps-function, fig.height=2.5, fig.width=8}
mu.b      <- 0.01 + bumps.f(t)
x         <- rpois(n,mu.b)
out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
out.smash <- smash.poiss(x,post.var = TRUE)
p6 <- create.signal.plot(t,x,mu.b) +
  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
print(p6)
```
